\documentclass{mycv}

\name[Alexey Izmailov]{Alexey Izmailov \small{Sc.B.}}
\address{Department of Applied Mathematics, Brown University \\ Providence, Rhode Island, USA, 02912}
\email{alizma@brown.edu}
\homepage{alizma.github.io}
\github{alizma}
\linkedin{alizma0}

\newcommand{\comment}[1]{}

\begin{document}

\maketitle%

\section{Technical \\ Coursework}

\begin{itemize}
    \item \textbf{Mathematics:} Applied Dynamical Systems, Topics in Abstract Algebra, Real Analysis, Statistical Inference, Linear Algebra, Applied Ordinary \& Partial Differential Equations, Single \& Multivariable Calculus, Advanced Classical Mechanics, Modern Physics (Stanford OHS)
    \item \textbf{Computer Science:} Fundamentals of Computer Systems, Blockchains and Cryptocurrencies, Accelerated Introduction to CS, AP CS A 
    \item \textbf{Directed Reading Programs:} Graduate Linear Algebra and Functional Analysis. Official write-up: \url{https://github.com/alizma/Spring2021_Functional_Analysis_Paper}.
\end{itemize}

\section{Professional \\ Experience}

\subsection{Teaching Assistant}[Brown University]
\begin{positions}
  \entry{Abstract Algebra (Math1530) Lead TA}{May 2021~--~Aug 2021}
\end{positions}
Provided weekly feedback on problem sets and held weekly office hours for a class of 30. 

\subsection{Everaise Academy}[Virtual]
\begin{positions}
  \entry{Curriculum Developer and TA}{Jun 2020~--~Present}
\end{positions}

\begin{itemize}
  \item Official Website: \href{everaise.org}{everaise.org}
  \item Composed several handouts on topics ranging from number theory to combinatorics and graded homework for ~100 students in the advanced topics course.
\end{itemize}

\section{Education}

\subsection{Brown University (In Progress)}[Rhode Island, USA]
\vspace{-\parskip}%
\begin{itemize}[label={}]
  \item Bs.C.\ in Applied Mathematics, Computer Science \printdate{Sep 2020~--~May 2024}
  \item Advisor: \href{https://www.dam.brown.edu/people/hdong/}{Prof.~Hongjie Dong}
\end{itemize}

\subsection{Brophy College Preparatory}[Arizona, USA]
\vspace{-\parskip}%
\begin{itemize}[label={}]
  \item High School Diploma with Distinction (Mathematics) \printdate{Aug 2016~--~May 2020}
\end{itemize}

\section{Awards}
\subsection{USAMTS Bronze (2017, 2019), Silver (2018) Winner}[Top 40 Nationally]
Active competitor in USA Mathematical Talent Search.

\subsection{USA National Chemistry Olympiad Semi-Finalist}[Top 1000 Nationally]
Competed in the premier chemistry competition for high school students in the USA.

\subsection{USA Computing Olympiad Silver Winner}[Top 5,000 Nationally]
Active competitor in premier computing olympiad for high school students in the USA. 

\subsection{AP National Scholar + National Distinction}[Top 1\% Nationally]
Awarded for high scores on 16 AP exams in high school.

\section{Personal \\ Projects} 

\subsection{Kibibyte: Text Editor in <1 KiB}[Programming]
Implemented in C with VT100 syntax highlighting, Vim-like scrolling, and edit history. Portable for all POSIX-compliant systems. See more: \url{https://github.com/alizma/kilo_text_editor}.

\section{Skills}

\begin{description}
  \item[Programming] GoLang, Solidity, C/C++, Python, \LaTeX, Bash, Markdown
  \item[Tools] Vim, Git, VSCode, NMap, Linux
  \item[Languages] English, Russian, Spanish (Conversational, 5 on AP)
\end{description}

\end{document}